The Ultraviolet Radiation Environment of a Tropical Megacity in Transition: Mexico City 2000-2019

### 2021-07-06 Paper_third_version/Article_UV_Mexico.tex
Add Madronich references

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{chemformula} % Formula subscripts using \ch{}
\usepackage[T1]{fontenc} % Use modern font encodings
\usepackage{lineno}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{multirow}

@@

The question of how air pollution alters the urban UV environment
(and~\emph{vice versa}) is not new, but studies have relied mostly on
numerical models \cite{Liu_1991,Sabziparvar_1998,Madronich_2011},
with relatively few available observations (e.g.,
\citet{McKenzie_2008}, \citet{Panicker_2009}, \citet{Palancar_2013},
reviewed by \citet{Bais_2015}). Increases in UV have been estimated as a consequence
of emission reductions over the last decades, e.g. in China,\citep{Hollaway_2019,Li_2018,Wang_2020}
and have led to less-than-expected
reductions in photochemical smog, in part due to stronger UV
photochemistry.\citep{Wang_2019,Gao_2020,Ma_2020}
Emission reductions have also occurred
globally during the 2020 COVID-19 pandemic,\citep{Bauwens_2020,Venter_2020}
but ground-level ozone in some polluted areas has actually
increased,\citep{Shi_2020,Le_2020} due at least in part to the increased UV
radiation. Unfortunately, the observational data base of relevant UV
radiation remains rather sparse to evaluate such model-derived
hypotheses.~~

@@

The UVI is recognized by the World Health and Meteorological
Organizations (WHO and WMO) as a standardized metric of UV
radiation\cite{who2002} for global public information. An advantage
of using the UVI as (one) measure of UV radiation is that it is being
increasingly observed or calculated and disseminated, enabling more
objective comparisons among seasons and locations. The UVI observations
from Mexico City, considered here, are an important element of this
global picture.

@@

With the aim to explore the relationship between UVI and air pollutants
levels, the hourly averages for ozone (O\textsubscript{3}), carbon
monoxide (CO), nitrogen dioxide (NO\textsubscript{2}), sulfur
dioxide~(SO\textsubscript{2}) and particle matter with diameter
sizes~\(\le\) 10 ~$\mu$m (PM\textsubscript{10}), were downloaded
from the SIMAT.\cite{atmosfrico} For purposes of assessing the
influence on the UV Index at solar noon, only values obtained between
11h and 15h CST were considered for the trends analysis. Pollutant
measurements are conducted by the SIMAT using regulatory-grade
commercial instruments. Measurement principles include ultraviolet
photometry (model 400E, Teledyne-API) for O\textsubscript{3},
chemiluminescence (model 200E, Teledyne-API) for NO\textsubscript{2}, UV
fluorescence (model 100E, Teledyne API) for SO\textsubscript{2}, and
infrared absorption (model 300E, Teledyne-API) for CO. The
PM\textsubscript{10} continuous mass concentration was measured with
Tapered Element Oscillating Microbalance (TEOM 1400AB or TEOM 1405 DF,
Thermo Scientific) monitors. Gaseous pollutant levels are reported in
ppb concentration units for O\textsubscript{3}, SO\textsubscript{2} and
NO\textsubscript{2}, and in ppm for CO. Particulate matter mass
concentration is reported in $\mu$g m\textsuperscript{-3} at local
conditions for temperature and pressure.

Aerosol optical depth at 340 nm was obtained from the Institute of
Geophysics of the National Autonomous University of Mexico (UNAM).
Measurements were conducted with a CIMEL sun photometer model CE-318,
which is an automatic sun-sky-scanning spectral radiometer of
the AErosol RObotic NETwork (AERONET~\citep{Holben_1998}). The data
Product Level 2.0 and 1.5 (only in 2019) were selected, and annual
averages AOD\textsubscript{340} were calculated along the period 2000-2019,
except for the year 2011 due to there were no measurements. A previous study of the AOD
behavior from 2000 to 2014 demonstrated that data gaps did not
significantly change the trends calculated for this.\citep{Carabali_2017}
Only 8\% of the data between the years 2014 and 2019 were missing.
The largest data gap occurred in 2018 when the instrument was returned for calibration.

@@

The UV Index data derived from satellite measurements of reflected radiance
were used for comparison with the ground-based measurements.
These data were provided by the Ozone Monitoring
Instrument (OMI)~on board of AURA-NASA satellite.\citep{dcio} OMI
is operated in cooperation between the Netherlands Agency for Aerospace
Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
OMI performs observations over a geographical area of 13$\times$24km\textsuperscript{2} at nadir. For
the coordinates (19.33°N, 99.18°W) and elevation (2268 m asl) of Mexico City,
the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
Measurements of the ozone profile and the attenuation by clouds are used via a
radiative transfer model to estimate the UVI at the ground.\cite{Tanskanen_2006}
The UV Index used for Mexico City corresponds to values at local noon time and clear sky
from OMUVB Level 2 OVP data product, version 1.3 and collection 3.

@@

The UV Index computed from satellite-based observations
over the period 2005-2019 is shown in
Figure~{\ref{485116}}. The satellite-derived UVIs vary
from 8 in winter to 16 in summer, both values being substantially higher
than the ground-based observations (ca. 7 for winter and 11 for summer,
see Fig.~{\ref{310112}}). We hypothesize that this
large difference between satellite-based estimation and ground-based
observation of the UV index is due to the intense air pollution of
Mexico City.~A rather similar behavior was detected in Santiago city,
Chile.\citep{Cabrera_2012}

Close inspection of Figure~{\ref{485116}} shows that the maximum values
are reached in June and July of each year.
While early OMI estimates of the UVI did not account for the boundary layer aerosol absorption,
the current version (1.3) includes the postcorrection by \citet{Arola_2009}
for absorbing aerosols based on global monthly aerosol climatology.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{lc}
    \hline
    \textbf{Conditions for estimation in June-July} & \textbf{UV Index} \\ \hline
    SIMAT average maxima 2000-2001                  & 9.9  $\pm$  1.2   \\ \hline
    SIMAT average maxima 2018-2019                  & 12.3 $\pm$  1.3   \\ \hline
    SIMAT maximum value reached in period 2000-2019 & 15.0              \\ \hline
    \begin{tabular}[c]{@{}l@{}}OMI maximum value reached in period 2005-2019,\\ not corrected for BL aerosols\end{tabular}                      & 16.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O3 0 ppb, NO2 0 ppb, SO2 0 ppb\end{tabular}                      & 16.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV pristine pollution\\ AOD 0.05, O3 10 ppb, NO2 0 ppb, SO2 0 ppb\end{tabular}                      & 15.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O3 50 ppb, NO2 20 ppb, SO2 1 ppb\end{tabular}                      & 12.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O3 70 ppb, NO2 40 ppb, SO2 20 ppb\end{tabular}                      & 10.2              \\ \hline
  \end{tabular}
  \caption{{UVI maxima for June-July: averages and standard deviation from ground-based data
        for the years 2018-2019 and 2000-2001. UVI maximum value reached in the period 2000-2019 for
        UVI ground-based and the same for satellite in the period 2005-2019. TUV calculations for different conditions.
      }}
  \label{table:TUVmodel}
\end{table}

@@

UV reductions by air pollutants are expected to be most severe near the
surface, while chemical reactions leading to photochemical smog occur
throughout the vertical extent of the BL.
Figure~{\ref{973680}} shows the vertical profiles of
photolysis coefficients (the reciprocals of photolytic lifetimes) for
two key reactions, the photolysis of O\textsubscript{3} to yield excited
oxygen atoms O(1D), and the photolysis of NO\textsubscript{2}. In the
absence of optically active pollutants, these coefficients would be
nearly independent of altitude in the BL. However, the presence of
pollutants leads to a strong decrease toward the surface, with notably
more severe reductions in 2000 compared to 2019.~While the specific
values shown in the figure are only illustrative for typical conditions,
routine daily air quality modeling should carefully account for the long
term variations in these photolysis coefficients.

@@

Two decades of observations in Mexico City demonstrate unequivocally
that air pollution reduces UV radiation at the ground. The ground-based
observations are well below data derived from satellite-based
observations. Although ideally both data sets should match,
the satellite has a limitation to seeing boundary layer absorbers.
When typical values of the pollutants: aerosols,
tropospheric ozone, and to a lesser extent NO\textsubscript{2}
and SO\textsubscript{2}, are included in a model (e.g. TUV), the
differences between satellite-derived and ground-based measured values
are explained and can be attributed quantitatively to individual
observed pollutants. Long term improvements in air quality over the last two decades,
are accompanied by statistically significant increases in the
observed UVI, again in good agreement with the model-predicted changes.

\begin{table}[H]
  \centering
  \begin{tabular}{lccccc}
    \hline
    \multicolumn{1}{c}{\multirow{2}{*}{Pollutant}} & \multicolumn{2}{c}{Year 2000} & \multicolumn{2}{c}{Year 2019} & 2000-2019                 \\ \cline{2-6}
    \multicolumn{1}{c}{}                           & poll. level (a)               & UVI (b)                       & poll. level & UVI   & (c) \\ \hline
    AOD                                            & 0.7                           & -3.7                          & 0.5         & -2.7  & 1.0 \\
    O\textsubscript{3} ppb (DU)                    & 70 (14)                       & -1.4                          & 50 (10)     & -1.0  & 0.4 \\
    NO\textsubscript{2} ppb                        & 40                            & -0.9                          & 20          & -0.5  & 0.4 \\
    SO\textsubscript{2} ppb                        & 30                            & -0.8                          & 1           & -0.04 & 0.8 \\ \hline
  \end{tabular}
  \caption{Contributions of individual pollutants to UV Index changes. (a) Values used one at the time, with the others held at zero. (b) UVI deviation from the zero-pollution value of 16.1 (from Table \ref{table:TUVmodel}). (c) 2019-2000 UVI change due to changes in each pollutant.}
  \label{table:year2000-2019}
\end{table}

@@

A limitation of the present work is our focus on daily maximum values,
which largely exclude cloud cover. Absorption within clouds can be
enhanced by the long path lengths of multiply scattered photons, so that accurate quantification of UV
effects of clouds in polluted environments remains a significant
challenge and interesting opportunity for future work.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{chemformula} % Formula subscripts using \ch{}
\usepackage[T1]{fontenc} % Use modern font encodings
\usepackage{lineno}
\usepackage{achemso}
\setkeys{acs}{maxauthors=20}
\setkeys{acs}{etalmode=truncate}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{multirow}

@@

The question of how air pollution alters the urban UV environment
(and~\emph{vice versa}) is not new, but studies have relied mostly on
numerical models \cite{Liu_1991,Sabziparvar_1998,Madronich_2011},
with relatively few available observations (e.g.,
\citet{McKenzie_2008}, \citet{Panicker_2009}, \citet{Palancar_2013},
reviewed by \citet{Bais_2015}). Increases in UV have been estimated as a consequence
of emission reductions over the last decades, e.g. in China,\citep{Hollaway_2019,Li_2018,Wang_2020}
and have led to less-than-expected
reductions in photochemical smog, in part due to stronger UV
photochemistry.\citep{Wang_2019,Gao_2020,Ma_2021}
Emission reductions have also occurred
globally during the 2020 COVID-19 pandemic,\citep{Bauwens_2020,Venter_2020}
but ground-level ozone in some polluted areas has actually
increased,\citep{Shi_2020,Le_2020} due at least in part to the increased UV
radiation. Unfortunately, the observational data base of relevant UV
radiation remains rather sparse to evaluate such model-derived
hypotheses.~~

@@

The UVI is recognized by the World Health and Meteorological
Organizations (WHO and WMO) as a standardized metric of UV
radiation\citep{who2002} for global public information. An advantage
of using the UVI as (one) measure of UV radiation is that it is being
increasingly observed or calculated and disseminated, enabling more
objective comparisons among seasons and locations. The UVI observations
from Mexico City, considered here, are an important element of this
global picture.

@@

With the aim to explore the relationship between UVI and air pollutants
levels, the hourly averages for ozone (O\textsubscript{3}), carbon
monoxide (CO), nitrogen dioxide (NO\textsubscript{2}), sulfur
dioxide~(SO\textsubscript{2}) and particle matter with diameter
sizes~\(\le\) 10 ~$\mu$m (PM\textsubscript{10}), were downloaded
from the SIMAT.\cite{pollutants_data} For purposes of assessing the
influence on the UV Index at solar noon, only values obtained between
11h and 15h CST were considered for the trends analysis. Pollutant
measurements are conducted by the SIMAT using regulatory-grade
commercial instruments. Measurement principles include ultraviolet
photometry (model 400E, Teledyne-API) for O\textsubscript{3},
chemiluminescence (model 200E, Teledyne-API) for NO\textsubscript{2}, UV
fluorescence (model 100E, Teledyne API) for SO\textsubscript{2}, and
infrared absorption (model 300E, Teledyne-API) for CO. The
PM\textsubscript{10} continuous mass concentration was measured with
Tapered Element Oscillating Microbalance (TEOM 1400AB or TEOM 1405 DF,
Thermo Scientific) monitors. Gaseous pollutant levels are reported in
ppb concentration units for O\textsubscript{3}, SO\textsubscript{2} and
NO\textsubscript{2}, and in ppm for CO. Particulate matter mass
concentration is reported in $\mu$g m\textsuperscript{-3} at local
conditions for temperature and pressure.

Aerosol optical depth at 340 nm was obtained from the Institute of
Geophysics of the National Autonomous University of Mexico (UNAM).
Measurements were conducted with a CIMEL sun photometer model CE-318,
which is an automatic sun-sky-scanning spectral radiometer of
the AErosol RObotic NETwork (AERONET~\citep{Holben_1998}). The data
Product Level 2.0 and 1.5 (only in 2019) were selected, and annual
averages AOD\textsubscript{340} were calculated for the period 2000-2019,
except for the year 2011 which contained large data gaps and was therefore not used.
A previous study of the AOD behavior from 2000 to 2014 demonstrated that data gaps did not
significantly change the trends calculated for this.\citep{Carabali_2017}
Only 8\% of the data between the years 2014 and 2019 were missing.
The largest data gap occurred in 2018 when the instrument was returned for calibration.

@@

The UV Index data derived from satellite-based measurements
were used for comparing to the ground-based measurements.
These data were provided by the Ozone Monitoring
Instrument (OMI)~on board of AURA-NASA satellite.\citep{dcio} OMI
is operated in cooperation between the Netherlands Agency for Aerospace
Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
OMI performs observations over a geographical area of 13$\times$24km\textsuperscript{2} at nadir. For
the coordinates (19.33°N, 99.18°W) and elevation (2268 m asl) of Mexico City,
the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths. The ozone column is estimated by differential absorption of several adjacent wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006} while clouds are estimated from the reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm, \citet{Tanskanen_2007}). A correction for absorbing aerosols is made using a global aerosol climatology\citep{Arola_2009}.
The UV Index used for Mexico City corresponds to values at local noon time and clear sky
from OMUVB Level 2 OVP data product, version 1.3 and collection 3.

@@

The UV Index computed from satellite-based observations
over the period 2005-2019 is shown in
Figure~{\ref{485116}}. The satellite-derived UVIs vary
from 8 in winter to 16 in summer, these values being substantially higher
than the ground-based observations (ca. 7 for winter and 11 for summer,
see Fig.~{\ref{310112}}). For both datasets the maximum values
are reached in June and July of each year. We hypothesize that this
large difference between satellite-based estimation and ground-based
observation of the UV index is due to the intense air pollution of
Mexico City.~A rather similar behavior was detected in Santiago city,
Chile.\citep{Cabrera_2012} Although the OMI data are corrected for climatological aerosol absorption\citep{Arola_2009}, this correction likely underestimates the absorption within the polluted Mexico City BL.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{lc}
    \hline
    \textbf{Conditions for estimation in June-July} & \textbf{UV Index} \\ \hline
    SIMAT average maxima 2000-2001                  & 9.9  $\pm$  1.2   \\ \hline
    SIMAT average maxima 2018-2019                  & 12.3 $\pm$  1.3   \\ \hline
    SIMAT maximum value reached in period 2000-2019 & 15.0              \\ \hline
    \begin{tabular}[c]{@{}l@{}}OMI maximum value reached in period 2005-2019,\\ not corrected for BL aerosols\end{tabular}                      & 16.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O\textsubscript{3} 0 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 16.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV pristine pollution\\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                      & 10.2              \\ \hline
  \end{tabular}
  \caption{{UVI maxima for June-July: averages and standard deviation from ground-based data
        for the years 2018-2019 and 2000-2001. UVI maximum value reached in the period 2000-2019 for
        UVI ground-based and the same for satellite in the period 2005-2019. TUV calculations for different conditions.
      }}
  \label{table:TUVmodel}
\end{table}

@@

UV reductions by air pollutants are expected to be most severe near the
surface, while chemical reactions leading to photochemical smog occur
throughout the vertical extent of the BL.
Figure~{\ref{973680}} shows the vertical profiles of
photolysis coefficients (the reciprocals of photolytic lifetimes) computed with the TUV model, for
two key reactions, the photolysis of O\textsubscript{3} to yield excited
oxygen atoms O(1D), and the photolysis of NO\textsubscript{2}. In the
absence of optically active pollutants, these coefficients would be
nearly independent of altitude in the BL. However, the presence of
pollutants leads to a strong decrease toward the surface, with notably
more severe reductions in 2000 compared to 2019.~While the specific
values shown in the figure are only illustrative for typical conditions,
routine daily air quality modeling should carefully account for the long
term variations in these photolysis coefficients.

@@

Two decades of observations in Mexico City demonstrate unequivocally
that air pollution reduces UV radiation at the ground. The ground-based
observations are well below values derived from satellite-based
observations. Although ideally both data sets should match,
the satellite has a limitation to seeing boundary layer absorbers.
When typical values of the pollutants: aerosols,
tropospheric ozone, and to a lesser extent NO\textsubscript{2}
and SO\textsubscript{2}, are included in a model (e.g. TUV), the
differences between satellite-derived and ground-based measured values
are explained and can be attributed quantitatively to individual
observed pollutants. Long term improvements in air quality over the last two decades,
are accompanied by statistically significant increases in the
observed UVI, again in good agreement with the model-predicted changes.

\begin{table}[H]
  \centering
  \begin{tabular}{lccccc}
    \hline
    \multicolumn{1}{c}{\multirow{2}{*}{Pollutant}} & \multicolumn{2}{c}{Year 2000} & \multicolumn{2}{c}{Year 2019} & 2000-2019                 \\ \cline{2-6}
    \multicolumn{1}{c}{}                           & poll. level (a)               & UVI (b)                       & poll. level & UVI   & (c) \\ \hline
    AOD                                            & 0.7                           & -3.7                          & 0.5         & -2.7  & 1.0 \\
    O\textsubscript{3} ppb (DU)                    & 70 (14)                       & -1.4                          & 50 (10)     & -1.0  & 0.4 \\
    NO\textsubscript{2} ppb                        & 40                            & -0.9                          & 20          & -0.5  & 0.4 \\
    SO\textsubscript{2} ppb                        & 30                            & -0.8                          & 1           & -0.04 & 0.8 \\ \hline
  \end{tabular}
  \caption{Contributions of individual pollutants to UV Index changes. (a) Values used one at the time, with the others held at zero. (b) UVI deviation from the zero-pollution value of 16.1 (from Table \ref{table:TUVmodel}). (c) 2000-2019 UVI change due to changes in each pollutant.}
  \label{table:year2000-2019}
\end{table}

@@
